Enhancing Accelerometer-based Activity Recognition with Capacitive Proximity Sensing

### 2012-06-21 Paper/Paper.tex
lines added

Figure \ref{fig:eugen_5} shows an example instance of preparing a bread with marmelade. It is notable that the acceleration data does not seem to provide any characteristic patterns, while the proximity sensor indicates a table, plate, or other objects in immediate distance. This activity showed a high improvement in the average f-measure by 10 \%, from 49.0 \% to 59.8 \%, when the capacitive proximity sensor is taken into account.

@@

The activity drinking water is depicted in Figure \ref{fig:eugen_7}. The participant took five nips from the glass, while leaving the hands lying on the table in between. These motions can be easily detected in the acceleration as well as proximity data. The accelerometer data shows that there periodic up- and down-movements while the capacitive proximity sensor delivers data that is associated to the proximity of the table.

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=1.00\textwidth]{../Auswertung/images/eugen_9.pdf}
	\caption{During the sleeping activity the data from both sensors remains constant. One draw conclusions about the coverage of the arm with either couchons, blankets or the proximity to the mattress.}
	\label{fig:eugen_9}
\end{figure}

@@

\section{Conclusion and Outlook}

>>>>

Figure \ref{fig:eugen_5} shows an example instance of preparing a bread with marmelade. It is notable that the acceleration data does not seem to provide any characteristic patterns, while the proximity sensor indicates a table, plate, or other objects in immediate distance. This activity showed a high improvement in the average f-measure by 10 \%, from 49.0 \% to 59.8 \%, when the data delivered by the capacitive proximity sensor is taken into account.

@@

The activity drinking water is depicted in Figure \ref{fig:eugen_7}. The participant took a few nips from the glass, while leaving the hands lying on the table in between. These motions can be easily detected in the acceleration as well as proximity data. The accelerometer data shows that there periodic up- and down-movements while the capacitive proximity sensor delivers data that is associated to the proximity of the table.

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=1.00\textwidth]{../Auswertung/images/eugen_9.pdf}
	\caption{During the sleeping activity the data from both sensors remains constant. One draw conclusions about the coverage of the arm with either couchons, blankets or the proximity to the mattress.}
	\label{fig:eugen_9}
\end{figure}
=======
\subsection{Evaluation Results}
\label{sect:evaluation}

@@

\section{Conclusion and Outlook}
\label{sect:conclusions}
